---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# openac

<!-- badges: start -->
<!-- badges: end -->

openac provides R wrappers around external, open-source affective-computing
tools — ffmpeg/ffprobe, OpenFace, openSMILE, and Whisper (via audio.whisper) —
so researchers can run them from a single, consistent R interface. It covers
tool discovery, installation, and configuration; audio/video preparation;
single-file and batch extraction (with parallelism and progress); and reading
each tool's output into a tidy tibble.

## Installation

You can install the development version of openac from
[GitHub](https://github.com/jmgirard/openac) with:

``` r
# install.packages("pak")
pak::pak("jmgirard/openac")
```

openac calls external command-line tools; install and register the ones you
need (e.g. `install_opensmile_mac()` / `install_opensmile_win()`, or point
openac at an existing install with `set_opensmile()`).

## Example

Extract acoustic features from a folder of audio files in parallel, then read
one result into a tidy tibble:

```{r example, eval = FALSE}
library(openac)

# Extract eGeMAPS features from every .wav under audio/ into features/.
os_extract_dir(
  indir = "audio",
  inext = "wav",
  aggdir = "features",
  config = "egemaps/v02/eGeMAPSv02"
)

# Read one aggregate output into a one-row-per-file tidy tibble.
feats <- os_read("features/clip01_agg.csv")
```

## Code of Conduct

Please note that the openac project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
