---
title: "Extracting audio from video with ffmpeg"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Extracting audio from video with ffmpeg}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  # The chunks below drive the ffmpeg binary over a folder of your own videos,
  # so they are shown for reference but not run when the vignette is built.
  eval = FALSE
)
```

This vignette shows how to pull the audio track out of a folder of video files
and write it to WAV files ready for acoustic analysis. `os_prep_audio()` wraps
**ffmpeg** to extract and convert an audio stream to the format openSMILE
expects; running it across many files in parallel is a matter of pairing it
with **furrr**.

```{r setup}
library(openac)
library(future)
library(furrr)
```

First confirm that openac can find a working ffmpeg (see `set_ffmpeg()` if not):

```{r}
check_ffmpeg()
```

List the input videos and derive a matching WAV path for each output:

```{r}
infiles <- list.files(
  path = "Z:/DynAMoS/Stimuli/Video",
  pattern = "\\.mp4$",
  full.names = TRUE,
  recursive = TRUE
)

# Mirror the input paths into an Audio/ folder, swapping the extension.
outfiles <- gsub("/Stimuli/Video/", "/Stimuli/Audio/", infiles)
outfiles <- gsub("\\.mp4$", ".wav", outfiles)
```

Set a parallel plan and map `os_prep_audio()` over the input/output pairs:

```{r}
plan("multisession", workers = 4)

future_walk2(
  .x = infiles,
  .y = outfiles,
  .f = os_prep_audio
)
```

For this common "every file in a directory" case you can skip the manual file
bookkeeping entirely and let `os_prep_audio_dir()` find, pair, and process the
files for you:

```{r}
os_prep_audio_dir(
  indir = "Z:/DynAMoS/Stimuli/Video",
  inext = "mp4",
  outdir = "Z:/DynAMoS/Stimuli/Audio",
  recursive = TRUE
)
```

Finally, confirm the WAV files were written:

```{r}
list.files(path = "Z:/DynAMoS/Stimuli/Audio", pattern = "\\.wav$")
```
