---
title: "Running opensmile in parallel"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Running opensmile in parallel}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  # The chunks below drive the openSMILE binary over a folder of your own
  # audio, so they are shown for reference but not run at build time.
  eval = FALSE
)
```

This vignette extracts acoustic features from a folder of WAV files with
**openSMILE**, in parallel via **furrr**. `os_extract()` can write both an
aggregate (functionals) CSV and a low-level-descriptor (per-frame) CSV per
file; `os_read()` later turns either into a tidy tibble.

```{r setup}
library(openac)
library(future)
library(furrr)
```

Confirm that openac can find a working openSMILE install (see `set_opensmile()`
if not, and `os_list_configs()` for the available feature configs):

```{r}
check_opensmile()
```

List the input audio and derive aggregate/LLD output paths for each file:

```{r}
infiles <- list.files(
  path = "Z:/DynAMoS/Stimuli/Audio",
  pattern = "\\.wav$",
  full.names = TRUE,
  recursive = TRUE
)

aggfiles <- gsub("/Stimuli/Audio/", "/Features/opensmile/", infiles)
aggfiles <- gsub("\\.wav$", "_agg.csv", aggfiles)
lldfiles <- gsub("_agg\\.csv$", "_lld.csv", aggfiles)
```

Set a parallel plan and map `os_extract()` over the input/output triples. The
`config` argument (forwarded to every call) selects the openSMILE feature set:

```{r}
plan("multisession", workers = 4)

future_pwalk(
  .l = list(infile = infiles, aggfile = aggfiles, lldfile = lldfiles),
  .f = os_extract,
  config = "egemaps/v02/eGeMAPSv02"
)
```

For the whole-directory case, `os_extract_dir()` finds and processes every
matching file for you:

```{r}
os_extract_dir(
  indir = "Z:/DynAMoS/Stimuli/Audio",
  inext = "wav",
  aggdir = "Z:/DynAMoS/Features/opensmile",
  config = "egemaps/v02/eGeMAPSv02",
  recursive = TRUE
)
```

Confirm the feature files were written, and read one into a tidy tibble:

```{r}
list.files(path = "Z:/DynAMoS/Features/opensmile", pattern = "\\.csv$")

feats <- os_read("Z:/DynAMoS/Features/opensmile/example_agg.csv")
```
