---
title: "Running openface in parallel"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Running openface in parallel}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  # The chunks below drive the OpenFace binary over a folder of your own
  # videos, so they are shown for reference but not run at build time.
  eval = FALSE
)
```

This vignette extracts facial-behavior features from a folder of videos with
**OpenFace**, running many files at once via **furrr**. `of_extract()` writes
one CSV of frame-level features per video; `of_read()` later turns any such CSV
into a tidy tibble.

```{r setup}
library(openac)
library(future)
library(furrr)
```

Confirm that openac can find a working OpenFace install (see `set_openface()`
if not):

```{r}
check_openface()
```

List the input videos and derive a matching CSV path for each output:

```{r}
infiles <- list.files(
  path = "Z:/DynAMoS/Stimuli/Video",
  pattern = "\\.mp4$",
  full.names = TRUE,
  recursive = TRUE
)

outfiles <- gsub("/Stimuli/Video/", "/Features/openface/", infiles)
outfiles <- gsub("\\.mp4$", ".csv", outfiles)
```

Set a parallel plan and map `of_extract()` over the input/output pairs. Extra
arguments (here the point-distribution model plus wild and multi-view modes)
are forwarded to every call:

```{r}
plan("multisession", workers = 4)

future_walk2(
  .x = infiles,
  .y = outfiles,
  .f = of_extract,
  pdm = TRUE,
  wild = TRUE,
  multiview = TRUE
)
```

For the whole-directory case, `of_extract_dir()` finds and processes every
matching file for you:

```{r}
of_extract_dir(
  indir = "Z:/DynAMoS/Stimuli/Video",
  inext = "mp4",
  outdir = "Z:/DynAMoS/Features/openface",
  recursive = TRUE,
  pdm = TRUE,
  wild = TRUE,
  multiview = TRUE
)
```

Confirm the feature files were written, and read one into a tidy tibble:

```{r}
list.files(path = "Z:/DynAMoS/Features/openface", pattern = "\\.csv$")

faces <- of_read("Z:/DynAMoS/Features/openface/example.csv")
```
